### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>
adding comments to reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

@@

@@

@@

>>>>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} We have implemented as suggested.}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} We explicitly indicate now that ESBMC-GPU applies MPOR, two-thread analysis, and state hashing in order to further simplify verification models.}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: which reference would you suggest to use here?}}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: what would be the next step to reduce the number of thread interleavings? Improve MPOR?}}
    \end{quote}
